---
title: "Middle-aged founders"
author: "Lukas Püttmann"
date: "4/26/2020"
output: html_document
---

Take data from the [paper](https://www.aeaweb.org/articles?id=10.1257/aeri.20180582)
"Age and High-Growth Entrepreneurship" by Pierre Azoulay, Benjamin F. Jones, 
J. Daniel Kim and Javier Miranda and visualize a dataset.

Import libraries:

```{r echo = F, message=F}
library(tidyverse)
library(haven)
```

Download the data to a temporary file location:

```{r}
temp <- tempfile()
download.file("https://www.aeaweb.org/doi/10.1257/aeri.20180582.data",temp)
```

Import the data for "Table A1: Founder Age – Perceptions from Media & Two Prominent VCs".

This defines a function which unzips the relevant file, import the Stata files 
and adds a column to describe the data source organization:

```{r}
import_org_dta <- function(org_name) {
  unz(temp, paste0("programs/", org_name,".dta")) %>% 
    read_dta() %>% 
    mutate(org = org_name) %>%
    select(org, everything())
}
```

Define a vector `orgs` holding the names of the organizations for which to 
import the data and then apply the above function for all of these and attach
the datasets below to form one dataset:

```{r}
orgs <- c("Matrix", "Sequoia", "TechCrunch", "Magazines")

perceptions <- lapply(X = orgs, FUN = import_org_dta) %>% 
  bind_rows()
```

Close tempororary connection:

```{r}
unlink(temp)
```

The resulting dataset holds the name of the organization, the name of the list
they created, the age of the founder and the company's name:

```{r}
perceptions
```

Plot the age of the founders and add a line marking the paper's estimate of 
45 years against it:

```{r}
ggplot(perceptions, aes(age, org, color = list)) +
  geom_jitter(alpha = 0.8, stroke = 0, size = 2.2) +
  labs(title = 'Founder Age – Perceptions from Media & Two Prominent VCs',
       subtitle = "Vertical line marks estimate from study (age = 45)",
       caption = 'Source: "Age and High-Growth Entrepreneurship" (2020) 
       by Azoulay, Jones, Kim and Miranda.', y = NULL, x = "Founder age", color = "List: ") +
  theme_minimal() +
  geom_vline(xintercept = 45) 
```

```{r}
ggsave("out_figures/founder_age_perceptions.jpg", width = 8, height = 5)
```

It's apparent that the media's and VC's perception of successful founders has 
younger people in mind than what the authors show in their paper.



